\bf The EPEC Model

### 2021-08-23 Documentation/EPEC_Model.tex
Improved documentation

\subsection{Critical Island Widths}
The critical full island width (in $r$) which must be exceeded before the electron temperature is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64g}
\frac{W_{T_e\,k} }{r_k}= 5.07\left(\frac{\chi_e}{\chi_{\parallel\,e}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
\end{equation}
where $\chi_e(r)$ is the perpendicular electron energy diffusivity profile, $\epsilon =r/R_0$, 
\begin{align}
\chi_{\parallel\,e}&= \frac{\chi_{\parallel\,e}^{\rm brag}\,\chi_{\parallel\,e}^{\rm max}}{\chi_{\parallel\,e}^{\rm brag}+\chi_{\parallel\,e}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,e}^{\rm brag} &= 1.13\,\tau_{ee}\,v_{T\,e}^{\,2},\\[0.5ex]
\chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}.
\end{align}
Equation~(\ref{e64g}) must be solved iteratively for $W_{T_e\,k}/r_k$.

@@

\section{Pressure Reduction} \label{a5}
The full width (in ${\mit\Psi}_N$)  of the magnetic separatrix of the island chain induced at the $k$th resonant surface is
\begin{equation}
\overline{W}_k = \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_k=4\left(A_{1\,k}\,\hat{\mit\Psi}_k\right)^{1/2},
\end{equation}
where 
\begin{equation}
\frac{d{\mit\Psi}_N}{dr} = \frac{r\,g}{R_0^{\,2}\,q\,|\hat{\mit\Psi}_p(0)|},
\end{equation}
$A_{1\,k}=A_1(r_k)$, $A_1 = 1/(\sigma\,|\hat{\mit\Psi}_p(0)|)$,  $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_{2\,k}\,W_k^{\,2}/8$ and $A_{2\,k} = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
On average, the presence of a magnetic island chain of full width $W_k$ at the $k$th resonant surface
causes the electron temperature, ion temperature,  and electron number density profiles to be flattened in  annular regions, centered on the
halfway points between the inner and outer radii of the island separatrices, of widths (in ${\mit\Psi}_N$)
\begin{align}
\delta_{T_e\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{T_e\,k}}\right),\\[0.5ex]
\delta_{T_i\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{T_i\,k}}\right),\\[0.5ex]
\delta_{n_e\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{n_e\,k}}\right),
\end{align}
respectively, where
\begin{align}
\overline{W}_{T_e\,k} &=  \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{T_e\,k},\\[0.5ex]
\overline{W}_{T_i\,k} &= \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{T_i\,k},\\[0.5ex]
\overline{W}_{n_e\,k} &= \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{n_e\,k}.
\end{align}

The total change in the plasma pressure interior to the $j$th resonant surface due to the temperature and
density flattening at the various resonant surfaces (assuming that the pressure at the LCFS is fixed) is
\begin{align}
{\mit\Delta}P_j &=\sum_{k=j,K} 
\left\{(F_1+F_3)\,\delta_{n_e\,k}+ F_2\,\delta_{T_e\,k}+F_4\,\delta_{T_i\,k} + (F_5+F_7)\,\delta_{n_e\,k}\,\overline{W}_k^{\,2}
\right.\nonumber\\[0.5ex]
&\phantom{++}\left.+F_6\, \delta_{T_e\,k}\,\overline{W}_k^{\,2}+ F_8\,\delta_{T_i\,k}\,\overline{W}_k^{\,2}+ (F_9+F_{11})\,\delta_{n_e\,k}^{\,3}
+ F_{10}\,\delta_{T_e\,k}^{\,3}+ F_{12}\,\delta_{T_i\,k}^{\,3}\right\}_{r_k},
\end{align}
where
\begin{align}
F_1 &=\frac{dn_e}{d{\mit\Psi}_N}\,T_e,\\[0.5ex]
F_2 &=\frac{dT_e}{d{\mit\Psi}_N}\,n_e,\\[0.5ex]
F_3 &=\frac{dn_i}{d{\mit\Psi}_N}\,T_i,\\[0.5ex]
F_4 &=\frac{dT_i}{d{\mit\Psi}_N}\,n_i,\\[0.5ex]
F_5& -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
F_6& -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
F_7& -\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
F_8& -\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
F_9&=\frac{T_e}{24}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{10}&=\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{11}&=\frac{T_i}{24}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{12}&=\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}},
\end{align} 
and we have neglected the impurity ion pressure.

>>>>

\subsection{Critical Island Widths}
The critical full island width (in $r$) which must be exceeded before the electron temperature is flattened within the
magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
\begin{equation}\label{e64g}
\frac{W_{T_e\,k} }{r_k}= 5.07\left(\frac{\chi_e}{\chi_{\parallel\,e}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
\end{equation}
where $\chi_e(r)$ is the perpendicular electron energy diffusivity profile, $\epsilon =r/R_0$, 
\begin{align}
\chi_{\parallel\,e}&= \frac{\chi_{\parallel\,e}^{\rm brag}\,\chi_{\parallel\,e}^{\rm max}}{\chi_{\parallel\,e}^{\rm brag}+\chi_{\parallel\,e}^{\rm max}},\\[0.5ex]
\chi_{\parallel\,e}^{\rm brag} &= \frac{1.55\,\tau_{ee}\,v_{T\,e}^{\,2}}{1+0.38\,Z_{\rm eff}},\\[0.5ex]
\chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}.
\end{align}
Equation~(\ref{e64g}) must be solved iteratively for $W_{T_e\,k}/r_k$.

@@

\section{Pressure Reduction} \label{a5}
The full width (in ${\mit\Psi}_N$)  of the magnetic separatrix of the island chain induced at the $k$th resonant surface is
\begin{equation}
\overline{W}_k = \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_k=4\left(A_{1\,k}\,\hat{\mit\Psi}_k\right)^{1/2},
\end{equation}
where 
\begin{equation}
\frac{d{\mit\Psi}_N}{dr} = \frac{r\,g}{R_0^{\,2}\,q\,|\hat{\mit\Psi}_p(0)|},
\end{equation}
$A_{1\,k}=A_1(r_k)$, $A_1 = 1/(\sigma\,|\hat{\mit\Psi}_p(0)|)$,  $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_{2\,k}\,W_k^{\,2}/8$, $A_{2\,k}=A_2(r_k)$, and $A_{2\,k} = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
On average, the presence of a magnetic island chain of full width $W_k$ at the $k$th resonant surface
causes the electron temperature, ion temperature,  and electron number density profiles to be flattened in  annular regions, centered on the
halfway points between the inner and outer radii of the island separatrices, of widths (in ${\mit\Psi}_N$)
\begin{align}
\delta_{T_e\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{T_e\,k}}\right),\\[0.5ex]
\delta_{T_i\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{T_i\,k}}\right),\\[0.5ex]
\delta_{n_e\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{n_e\,k}}\right),
\end{align}
respectively, where
\begin{align}
\overline{W}_{T_e\,k} &=  \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{T_e\,k},\\[0.5ex]
\overline{W}_{T_i\,k} &= \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{T_i\,k},\\[0.5ex]
\overline{W}_{n_e\,k} &= \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{n_e\,k}.
\end{align}

The total change in the plasma pressure interior to the $j$th resonant surface due to the temperature and
density flattening at the various resonant surfaces (assuming that the pressure at the LCFS is fixed) is
\begin{align}
{\mit\Delta}P_j &=\sum_{k=j,K} 
\left\{(F_1+F_3)\,\delta_{n_e\,k}+ F_2\,\delta_{T_e\,k}+F_4\,\delta_{T_i\,k} + (F_5+F_7)\,\delta_{n_e\,k}\,\overline{W}_k^{\,2}
\right.\nonumber\\[0.5ex]
&\phantom{++}\left.+F_6\, \delta_{T_e\,k}\,\overline{W}_k^{\,2}+ F_8\,\delta_{T_i\,k}\,\overline{W}_k^{\,2}+ (F_9+F_{11})\,\delta_{n_e\,k}^{\,3}
+ F_{10}\,\delta_{T_e\,k}^{\,3}+ F_{12}\,\delta_{T_i\,k}^{\,3}\right\}_{r_k},
\end{align}
where
\begin{align}
F_1 &=\frac{dn_e}{d{\mit\Psi}_N}\,T_e,\\[0.5ex]
F_2 &=\frac{dT_e}{d{\mit\Psi}_N}\,n_e,\\[0.5ex]
F_3 &=\frac{dn_i}{d{\mit\Psi}_N}\,T_i,\\[0.5ex]
F_4 &=\frac{dT_i}{d{\mit\Psi}_N}\,n_i,\\[0.5ex]
F_5&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
F_6&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
F_7& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
F_8& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
F_9&=\frac{T_e}{24}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{10}&=\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{11}&=\frac{T_i}{24}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{12}&=\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}},
\end{align} 
and we have neglected the impurity ion pressure.
